---
title: "CV - bttomio"
first: "ok"
date: "Updated `r Sys.Date()`"
output:
  pagedown::html_paged:
    self_contained: false
    css: [anderson-cv.css]
    number_sections: false
links-to-footnotes: false
---

```{r setup, include=FALSE}
library(tidyverse)
library(lubridate)
library(knitr)
opts_chunk$set(echo = FALSE)
options(knitr.kable.NA = '')

#### cv entries #####
cv_entries <- readxl::read_xlsx(here::here("data", "cv_entries.xlsx"))

#### publications #####
pubs <- readxl::read_xlsx(here::here("data", "pubs.xlsx")) %>% 
  arrange(order) %>% 
  select(-order)

pubs <- map_df(pubs, ~gsub("\\.$", "", .x))

```


```{r}
PDF <- TRUE # Set to TRUE when rendering to PDF via pagedown::chrome_print()
if(PDF) {
  header <- '
  View online
  <a href="https://bttomio.github.io/cv/" class="icon-block">
      <i class="fas fafooter fa-globe"></i>
  </a>
  '
} else {
  header <- '
  Download PDF
  <a href="https://bitly.com/bttomiocv" class="icon-block">
      <i class="fas fafooter fa-download"></i>
  </a>
  '
}
```


<div class = "download">
```{r results = "asis"}
cat(header)
```

</div>

<div class = "footer",>
  <a href="mailto:bttomio@furb.br" class="icon-block">
      <i class="fas fafooter fa-envelope"> </i>
  </a>
  |
  <a href="https://bttomio.github.io" class="icon-block">
      <i class="fas fafooter fa-globe"> </i>
  </a>
  |
  <a href="https://scholar.google.com.br/citations?user=wrMYaNUAAAAJ&hl" class="icon-block">
      <i class="fab fafooter fa-google"> </i>
  </a>
  |
  <a href="https://www.linkedin.com/in/bttomio/" class="icon-block">
      <i class="fab fafooter fa-linkedin"> </i>
  </a>
  |
  <a href="https://www.github.com/bttomio" class="icon-block">
      <i class="fab fafooter fa-github"> </i>
  </a>

</div>


<div id = "block_container">

<div class = "first", id="bloc1">Bruno Thiago</div>  
<div class = "last", id="bloc2">Tomio</div>

</div>

<div id = "position", class = "position">
<a href="https://goo.gl/maps/AMsFNFoCnSwF7ymu6"> <span style="color: #454545"><i class="fas fa-map-marker-alt"></i></span> Grenoble, France </a>
| <a href="mailto:bttomio@furb.br"> <span style="color: #454545"><i class="fas fa-envelope"></i></span> bttomio@furb.br </a>
| <a href="https://bttomio.github.io"> <span style="color: #454545"><i class="fas fa-globe"></i></span> https://bttomio.github.io </a>
</div>



<div class="grid-container">


</div>

## Education {.education .nohead}

```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what),
         what = ifelse(!is.na(url), 
                       paste0("[", what, "](", url, ")"), 
                       what)
         ) %>% 
  mutate(year = str_c(year_begin, " --- ", year_end)) %>% 
  select(year, what) %>% 
  kable()
```

## Brief Professional History {.history .nohead}

```{r}
cv_entries %>% 
  filter(type == 'history') %>% 
  mutate(what = paste0("<span style= 'font-weight: 500'>",
                       what, 
                       "</span>"),
    what = paste0(what, ", ", where),
         what = gsub("NA", "", what),
         what = gsub(", $", "", what)) %>% 
  mutate(year = str_c(year_begin, 
                      " --- ", 
                      ifelse(is.na(year_end), "", year_end))) %>% 
  select(year, what) %>% 
  kable()
```

## Skills


<div style="float: left; width: 60%;">
<b>Languages</b>
<br><i>English</i>:  Fluent/advanced (C1-C2).
<br><i>French</i>:  Fluent/advanced (C1-C2).
<br><i>Portuguese</i>: Native speaker.
</div>

<div style="float: right; width: 40%;">
<b>Programming</b>
<br><i>R</i>
<br><i>Stata</i>
<br><i>EViews</i>
</div>

# Research

<div class = "inote">
Icons link to additional content  
</div>


## Peer-Reviewed Publications (Selected) {.prpa .nohead}

<div class = "hangingindent">

```{r}
make_cite <- function(authors,	year,	title,	journal = NULL,	volume = NULL,	
                      issue = NULL,	pages = NULL,	doi = NULL,	url = NULL,
                      book = NULL, place_published = NULL, conference = NULL,
                      poster = NULL, conf_loc = NULL, annual_meeting = NULL,
                      version = NULL,...) {
  
  if(!is.null(journal)) {
    journal <- paste0("*", journal, "*.")
  }
  
  if(!is.null(volume)) {
    volume <- paste0("*", volume, "*,")
  }
  
  if(!is.null(issue)) {
    volume <- paste0(gsub(",", "", volume), "(", issue, "),")
  }
  if(!is.null(doi) & !is.null(url)) {
    doi <- paste0("[doi: ", doi, "](", url, ")")
  }
  if(!is.null(pages)) {
    if(!is.null(book)) {
      pages <- paste0("(pp. ", pages, ").")
    }
    else {
     pages <- paste0(pages,".") 
    }
  }
  if(!is.null(book)) {
    book <- paste0("*", book, "*")
  }
  if(!is.null(conference)) {
    title <- paste0("*", title, "*")
    if(is.null(poster)) {
      if(annual_meeting) {
        conference <- paste0("Presentation at the annual ", conference, ".")
      }
      else {
        conference <- paste0("Presentation at the ", conference, ".")
      }
    }
    else if(poster) {
      if(annual_meeting) {
       conference <- paste0("Poster presented at the annual meeting of the ", 
                            conference,
                            ", ", 
                            conf_loc,
                            ".") 
      }
      else {
        conference <- paste0("Poster presented at the ", 
                             conference, 
                             ", ", 
                             conf_loc, 
                             ".") 
      }
    }
    else {
       if(annual_meeting) {
          conference <- paste0("Paper presented at the annual meeting of the ", 
                            conference, 
                            ", ", 
                            conf_loc,
                            ".") 
      }
      else {
        conference <- paste0("Paper presented at the ", 
                             conference, 
                             ",", 
                             conf_loc,
                            ".") 
      }
    }
  }
  if(!is.null(version)) {
    version <- paste0("R package version ", version, ".")
  }
  authors <- gsub(
    "Anderson, D\\.?",
    "<span style= 'font-weight: 500'>Anderson, D.</span>", 
    authors)
   
  paste(authors, 
        paste0("(", year, ")."), 
        paste0(title, "."),
        version, 
        conference,
        journal, 
        volume,
        book,
        pages, 
        doi,
        place_published)
}

prpas <- pubs %>% 
  filter(type == "prpa") %>% 
  select(-type) 

each_cite <- split(prpas, seq_len(nrow(prpas)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

fa_doc <- ifelse(
  !is.na(prpas$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         prpas$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(prpas$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         prpas$git_repo, 
         ")"
         ),
  ""
  )

pubs_tbl <- tibble(year = prpas$year,
                  count = paste0(seq(length(formatted_cites), 1), "."),
                  cites = paste(unlist(formatted_cites), fa_doc, fa_git)) 

pubs_tbl <- pubs_tbl %>% 
  group_by(year) %>%
  mutate(count_within_year = 1:n()) %>% 
  ungroup() %>% 
  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
  select(-count_within_year)

pubs_tbl <- dplyr::select(pubs_tbl, cites)
  
kable(pubs_tbl[1:4, ])
```

</div>

## Book chapters {.submitted .nohead}

<div class = "hangingindent">

```{r}
chapters <- pubs %>% 
  filter(type == "book-chapter") %>% 
  select(-type)

each_cite <- split(chapters, seq_len(nrow(chapters)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

chapters_tbl <- tibble(count = paste0(seq(length(formatted_cites), 1), "."),
                        cites = unlist(formatted_cites)) 

chapters_tbl <- dplyr::select(chapters_tbl, cites)
  
kable(chapters_tbl)

```

</div>

## Conference Presentations (Selected) {.prpa .nohead}

<div class = "hangingindent">

```{r}
confs <- pubs %>% 
  filter(type == "conference") %>% 
  select(-type)

fa_doc <- ifelse(
  !is.na(confs$full_paper_link), 
  paste0('[<i class="fas falink2 fa-file-alt"></i>](', 
         confs$full_paper_link, 
         ")"
         ),
  ""
  )

fa_git <- ifelse(
  !is.na(confs$git_repo), 
  paste0('[<i class="fab falink2 fa-github"></i>](', 
         confs$git_repo, 
         ")"
         ),
  ""
  )

fa_pres <- ifelse(
  !is.na(confs$slides_link), 
  paste0('[<i class="fas falink3 fa-chalkboard-teacher"></i>](', 
         confs$slides_link, 
         ")"
         ),
  ""
  )


each_cite <- split(confs, seq_len(nrow(confs)))
empties <- map(each_cite, ~map_lgl(.x, is.na))

cites <- map2(each_cite, empties, ~.x[ ,!.y])
formatted_cites <- map(cites, ~do.call(make_cite, .x)) 

conf_tbl <- tibble(year = confs$year,
                   count = paste0(seq(length(formatted_cites), 1), "."),
                   cites = paste(unlist(formatted_cites), 
                                 fa_doc, 
                                 fa_pres, 
                                 fa_git)
)
  

conf_tbl <- conf_tbl %>% 
  mutate(year = parse_number(year)) %>% 
  group_by(year) %>%
  mutate(count_within_year = 1:n()) %>% 
  ungroup() %>% 
  mutate(year = ifelse(count_within_year == 1, year, "")) %>% 
  select(-count_within_year)

conf_tbl <- dplyr::select(conf_tbl, cites)

kable(conf_tbl[seq(1, 4), ])
```

</div>

## Ad hoc reviewer {.nohead}

<span style= 'color: #5F6A6A;'>I have served as a peer reviewer for the following journals:</span>

<div class = "adhoc">

```{r}
reviewer <- cv_entries %>%
  filter(type == "peer-reviewer") %>%
  select(what) %>%
  mutate(index = c(rep(1, floor(nrow(.)/2)), 
                   rep(2, nrow(.) - floor(nrow(.)/2))
                   ))


jou1 <- reviewer$what[reviewer$index == 1]
jou2 <- reviewer$what[reviewer$index == 2]

if(length(jou1) < length(jou2)) {
  jou1 <- c(jou1, NA)
}
if(length(jou2) < length(jou1)) {
  jou2 <- c(jou2, NA)
}

data.frame(jou1, jou2) %>%
  kable()
```

</div>

## References {.nohead}

<span style= 'color: #5F6A6A;'>Contact information is available upon request.</span>